Variance reduction for MCMC methods via martingale representations

### 2020-03-10 aap/Revision/vr-mcmc-revision-new.tex
theorem 4 update

\paragraph{Variance:} An upper bound for the variance of the classical estimator~\eqref{eq:29032018a2}
under {\bf (H1)} and {\bf (H2)} is derived in Section.  In particular, for any bounded function $f,$
\begin{equation}
\label{eq:var-mc}
\PVar[\pi_n^N(f)]\lesssim (n\gamma)^{-1} \eqsp,
\end{equation}
where $\lesssim$ stands for inequality up to a constant depending on constants $L_U,$ $m_U,$  $M_U$ and $\|f\|_\infty.$
One of the main results of this paper is the following  upper bound for the variance of $\pi_{K,n}^{N}(f).$

@@

A_{s,\mathbf{k}}(x)=\gamma^{|\mathbf{k}'|/2}\frac{\sqrt{(\mathbf{k}-\mathbf{k}')!}}{\sqrt{\mathbf{k}!}}\mathsf{E}\left[ \partial_{Z_1}^{\mathbf{k}'} F(x,Z_1,\ldots,Z_s) \mathbf{H}_{\mathbf{k}-\mathbf{k}'}(Z_{1})\right]

@@

where $F_s(x,Z_1,\ldots,Z_s)=\sum_{r=0}^s f(X^x_r)$ and $\partial_{Z_1}^{\mathbf{k}'}$

@@

\sum_{\mathbf{k}\colon\|\mathbf{k}\|\geq K+1} A^2_{s,\mathbf{k}}(x)\leq \sum_{I\subseteq\{1,\ldots,d\},\, I\neq \emptyset}

@@

\PVar_x \left( \sum_{p=1}^{s}\partial_{Z_{1}}^{\mathbf{K}_I}f\left(X_{p}\right)

@@

@@

for some constant $C$ not depending on $q$ and $V(x) = 1 + \|x\|^2$.

>>>>

\paragraph{Variance:} An upper bound for the variance of the classical estimator~\eqref{eq:29032018a2}
under {\bf (H1)} and {\bf (H2)} is derived in Section ??. \denis{Insert} In particular, for any bounded function $f,$
\begin{equation}
\label{eq:var-mc}
\PVar[\pi_n^N(f)]\lesssim (n\gamma)^{-1} \eqsp,
\end{equation}
where $\lesssim$ stands for inequality up to a constant depending on constants $L,$ $m,$  $M$ and $\|f\|_\infty.$
One of the main results of this paper is the following  upper bound for the variance of $\pi_{K,n}^{N}(f).$

@@

A_{q,\mathbf{k}}(x)=\gamma^{|\mathbf{k}'|/2}\frac{\sqrt{(\mathbf{k}-\mathbf{k}')!}}{\sqrt{\mathbf{k}!}}\mathsf{E}\left[ \partial_{Z_1}^{\mathbf{k}'} F(x,Z_1,\ldots,Z_q) \mathbf{H}_{\mathbf{k}-\mathbf{k}'}(Z_{1})\right]

@@

where $F_q(x,Z_1,\ldots,Z_q)=\sum_{r=0}^q f(X^x_r)$ and $\partial_{Z_1}^{\mathbf{k}'}$

@@

\sum_{\mathbf{k}\colon\|\mathbf{k}\|\geq K+1} A^2_{q,\mathbf{k}}(x)\leq \sum_{I\subseteq\{1,\ldots,d\},\, I\neq \emptyset}

@@

\PVar \left( \sum_{p=1}^{q}\partial_{Z_{1}}^{\mathbf{K}_I}f\left(X_{p}^x\right)

@@

\right)\leq C_{K}\gamma^{-1}(1+V(x)), \quad V(x) = 1 + \|x\|^2

@@

for some constant $C_K$ not depending on $q$ and $\gamma$.
